Testing the JD-R theory via O*Net definitional specification

### 2022-10-11 SIOP2023/SIOP_PROCESS.tex
PROCESS for SIOP (just a couple of notes left - do we want to change "stress" to "strain" throughout?)

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Testing the JD-R Theory: Using the Content of the O*Net},
  pdfauthor={Alicia A. Stachowski1 \& John T. Kulas2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Testing the JD-R Theory: Using the Content of the O*Net}
\author{Alicia A. Stachowski\textsuperscript{1} \& John T. Kulas\textsuperscript{2}}
\date{}

\shorttitle{SIOP\_Hindrances-Resources Interaction}

@@

The Job Demands-Resources Theory {[}JD-R; Demerouti et al. (2001){]} has received wide support across contexts and varied research questions. We extend the literature by 1) exploring the interaction between \emph{perceptions} of job demands and resources on the outcome of stress using job characteristics in the popular O*Net and 2) by considering also the appraisal of demands as challenge or hindrance stressors. Here, respondents made a series of evaluations that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net, is provided.

\hypertarget{the-job-demands-resources-theory}{%
\subsection{The Job demands-Resources Theory}\label{the-job-demands-resources-theory}}

The job demands-resources theory is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001). One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands, which are thoroughly documented by job in O*Net. \emph{Resources} are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). \emph{Demands}, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al. (2001)).

Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation {[}resulting from resources; Bakker and Demerouti (2014){]}. Demanding job characteristics are frequently associated with negative outcomes (e.g., Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007). However, a related line of research emphasizes a distinction between two types of demands - that of ``challenge'' and ``hindrance'' demands, suggesting that employees may evaluate stressors in different ways.

\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
\subsection{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}

@@

Searle and Auton (2015) note that much of our research on workplace demands is based on apriori classifications of demands. For instance, we assume that generally, time pressure is a negative demand on an employee. However, the stress experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary. Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments. An appraisal is the cognitive process whereby meaning is assigned to a stimulus. If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind. This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable (Lazarus \& Folkman, 1984). As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.

We next consider the empirical evidence on the subjective nature of demands and resources. First, as hinted at above, some research suggests that job demands and resources may not be universally appraised or assigned as such. Starting with job demands, Webster et al. (2011) studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being \emph{both} a challenge and hindrance to different degrees. While their study not did include resources, it documents individual differences in how people perceive stressors at work. Although not the primary focus of their paper, Sonnega et al. (2018) compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net. Correlations physical demand (\emph{r} = .52), stress (\emph{r} = .10), and need for intense concentration (\emph{r} = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think. While the above two studies provide evidence for variability in perception of demands, Schmitz et al. (2019) captured subjective and objective resources in their study of retirement. Correlations of composite variables between subjective and objective measures for the resources of autonomy (\emph{r} = .12. p \textgreater{} .01), recognition of work (\emph{r} = .07, p \textgreater{} .01), and decision freedom (\emph{r} = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap. We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees. Downes et al. (2021) meta-analysis addresses this reality in depth, although it is beyond the scope of this project.

Thus, while it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that individual appraisal is an important consideration. It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating. Here, we asked respondents to rate all of the job characteristics in terms of hindrances, challenges, and resources.

\hypertarget{value-of-exploring-the-onet-resource}{%
\subsection{Value of exploring the O*Net Resource}\label{value-of-exploring-the-onet-resource}}

First, the Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated. These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice. It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion. We utilized statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).

@@

These data were taken from a larger study on JD-R theory as it applies to O*NET items, particularly Proposition 3 of the JD-R model - that job resources can buffer the impact of job demands on strain. The interaction between job resources and demands has been heavily studied with regard to a range of outcomes. For example Bakker et al. (2010) found that resources (e.g., learning opportunities, autonomy, leader support) predicted both task enjoyment and organizational commitment even under conditions of high demands. Much of the research, however, has focused on stress/strain and burnout outcomes. For example, Bakker et al. (2005) found that job resources lessen the impact of demands on burnout in a large sample of employees working in higher education, and Xanthopoulou et al. (2007) found similar patterns in a sample of home care organization employees.

Our specific interest in the current study is in whether or not \emph{perceptions} of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources. The Job demands-Resources theory would suggest resources would buffer this relationship. In fact, a rather large body of empirical evidence supports this assertion (e.g., see Bakker \& Demerouti, 2017 for a historical review). We do have some existing evidence that this occurs with other outcomes beyond stress. For example, Tadić et al. (2015) found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers. Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement. Here, we propose that perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress. The following two predictions are made:

\emph{H1. There is a positive relationship between perceived hindrance stressors and stress.}

\emph{H2. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.}

@@

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

We sampled from a Prolific panel, resulting in 785 individuals who initially 166 accessed the survey link. Of those, 112 indicated that they were not interested, had more 167 than 200 missing responses, or had 20 or more identical consecutive sequential responses 168 (Yentes \& Wilhelm, 2021). There were a total of 568 respondents, of which 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.Their ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53). Over half, 52.58\% identified as female, and 46.83\% identified as male.

@@

To guage resources and hindrances, we used 98 statements taken directly from O*Net's ``activity'' and ``context'' classifications. Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high). Subsequent to these self-evaluations, respondents were asked to rate elements in terms of resources (``\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development''), challenges, (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains'') and hindrances (``\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment''). For each category (e.g., resources), a means was computed across items that applied to one's role, and thus, mean scores could range from 1 to 5.

@@

Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al. (2019)) captured stress (e.g., ``How often have you had problems relaxing because of your job?''). Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time''. Alpha was .85 in this sample.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

The data presented here were part of a larger study on the Job-demands Resources Model using O*Net. Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them. For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge. Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

\begin{tablenotes}[para]
\normalsize{\textit{Note.} R\textasciicircum{}2 etc here}
\end{tablenotes}

@@

Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 (Hayes, 2022, see Table \ref{tab:table}). First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, \emph{p} = .020. The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, \emph{p} = .061, providing tentative support for H2. As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources. As such, these results provide some evidence that the resources do moderate the relationship between hindrance stressors.

@@

\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K.others. (2001). Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Testing the JD-R theory via O*Net definitional specification},
  pdfauthor={Alicia A. Stachowski1 \& John T. Kulas2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Testing the JD-R theory via O*Net definitional specification}
\author{Alicia A. Stachowski\textsuperscript{1} \& John T. Kulas\textsuperscript{2}}
\date{}

\shorttitle{Hindrances-Resources Interaction}

@@

The Job Demands-Resources Theory (JD-R, Demerouti et al., 2001) has received wide support across contexts and varied research questions. We extend the literature by 1) exploring the interaction between job demands and resources on the experience of stress using O*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors. Here, respondents made a series of evaluations that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of challenge and hindrance stressors. Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net, is provided.

\hypertarget{the-job-demands-resources-theory}{%
\subsection{The Job Demands-Resources Theory}\label{the-job-demands-resources-theory}}

The job demands-resources theory is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001). One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics (which are thoroughly documented across many jobs within O*Net) via \emph{resources} and \emph{demands}. Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al. (2001)).

Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation (resulting from resources, Bakker \& Demerouti, 2014). Demanding job characteristics are frequently associated with negative outcomes (e.g., Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007). However, a related line of research emphasizes a further distinction between two types of demands - that of \emph{challenge} and \emph{hindrance} demands, suggesting that employees may evaluate stressors in different ways.

\hypertarget{the-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
\subsection{The Subjective Nature of Demands and Resources: The Role of Appraisal}\label{the-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}

@@

Searle and Auton (2015) note that much of our research on workplace demands is based on \emph{a priori} classifications of demands. For instance, we assume that generally, time pressure is a negative demand on an employee. However, the stress experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary. Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments. An appraisal is the cognitive process whereby meaning is assigned to a stimulus. If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind. This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable (Lazarus \& Folkman, 1984). As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.

We next consider the empirical evidence on the subjective nature of demands and resources. First, as hinted at above, some research suggests that job demands and resources may not be universally appraised or assigned as such. Starting with job demands, Webster et al. (2011) studied workload, role ambiguity, and role conflict, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being \emph{both} a challenge and hindrance to different degrees. While their study not did include resources, it does document individual differences in how people may perceive stressors at work.

\begin{quote}
Although not the primary focus of their paper, Sonnega et al. (2018) compared self-reported (subjective) ratings of the degree of physical demands, stress, and a need for intense concentration from the Health and Retirement Study with objective ratings from O*Net. Correlations physical demand (\emph{r} = .52), stress (\emph{r} = .10), and need for intense concentration (\emph{r} = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
\end{quote}

While the above two studies provide evidence for variability in how workers view \emph{demands}, Schmitz et al. (2019) went on to further capture subjective and objective \emph{resources} in their study of retirement.

\begin{quote}
{[}Same as above{]}: Correlations of composite variables between subjective and objective measures for the resources of autonomy (\emph{r} = .12. p \textgreater{} .01), recognition of work (\emph{r} = .07, p \textgreater{} .01), and decision freedom (\emph{r} = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
\end{quote}

We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees. Downes et al. (2021) meta-analysis addresses this reality in depth, although a broader current elaboration is beyond the scope of this SIOP presentation.

Thus, while it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration. It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating. In order to account for this possibility of ``non-exclusivity'', we asked our respondents to rate all relevant job characteristics in terms of their status as hindrances, challenges, and resources.

\hypertarget{value-of-consulting-onet}{%
\subsection{Value of consulting O*Net}\label{value-of-consulting-onet}}

The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated. These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations. It is also often useful to employers by providing them with information that may be helpful in a job analysis context. For the current study, we focused on statements taken from O*NET's \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to characteristics of work such as how often a worker interacts with others or engages in physical labor). From a job analytic lens, these descriptors are written more broadly than a task statement, and would most likely be classified by most job analysts as ``responsibilities''.

@@

The data we describe here represents a subset taken from a larger study on JD-R theory and its integration within the O*NET framework. For SIOP, we specifically investigate Proposition 3 of the JD-R model - that job resources can buffer the impact of job demands on strain. The interaction between job resources and demands has been heavily studied with regard to a range of outcomes. For example Bakker et al. (2010) found that resources (e.g., learning opportunities, autonomy, leader support) predicted both task enjoyment and organizational commitment even under conditions of high demands. In fact, a rather large body of empirical evidence supports this assertion (e.g., see Bakker \& Demerouti, 2017 for a historical review). Much of the research, however, has focused on stress/strain and burnout outcomes. For example, Bakker et al. (2005) found that job resources lessen the impact of demands on burnout in a large sample of employees working in higher education, and Xanthopoulou et al. (2007) found similar patterns in a sample of home care organization employees.

Our unique contribution in the current study is in whether or not \emph{perceptions} of demands as hindrances or challenges are related to experienced stress, and whether or not this relationship is moderated by the presence of resources. We do have some existing evidence that this occurs with other outcomes beyond stress. For example, Tadić et al. (2015) found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers. Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement. With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress. The following two predictions are made:

\begin{quote}
\emph{H1}. There is a positive relationship between perceived hindrance stressors and stress.
\end{quote}

\begin{quote}
\emph{H2}. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.
\end{quote}

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance for that characteristic. For characteristics that \emph{were} implicated as being relevent for their job, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge. Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

785 individuals initially accessed the survey link. Of those 785, several indicated that they were not interested after learning more about the project, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses. Any individual respondent who fell into any of these three areas of concern was removed from the initial data frame, resulting in a final realized sample of 568. 13.57\% of these individuals had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Their ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53). Over half (52.58\%) identified as female, and 46.83\% identified as male.

@@

To guage resources and hindrances, we used 98 statements taken directly from O*Net's ``activity'' and ``context'' classifications. Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high). Subsequent to self-evaluations regarding whether or not the characteristic was applicable to one's job, the respondents were asked to rate germane elements in terms of it's experience as a resource (``\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development''), challenge, (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains'') as well as hindrance (``\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment''). For each category (e.g., resources), a mean score was computed that indicated the across items that applied to one's role, and thus, mean scores could range from 1 to 5.

@@

Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) captured stress (an example item is: ``How often have you had problems relaxing because of your job?''). Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time''. Alpha was .85 in this sample.

@@

\begin{tablenotes}[para]
\normalsize{\textit{Note.} $R^2$ here}
\end{tablenotes}

@@

Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 (Hayes, 2022, see Table \ref{tab:table}). First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, \(F_{(3, 564)}\) = 3.29, \emph{p} = .020. The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, \(F_{(3, 564)}\) = 3.51, \emph{p} = .061, providing marginal support for H2. As can be seen in Figure \ref{fig:analyses}, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources. As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of stress.

@@

\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K., et al. (2001). Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.
